Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2001-01-01 paper.tex
Add table of L, R, <eps> for RT vs M1

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
Total and relative number and energy luminosities for the disk evolved
in \cite{fouc2016-m1_evolve_n}.
Agreement better than 10\%.
\todo{put in table comparison M1 and RT}

>>>>

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
Total and relative number and energy luminosities for the disk evolved
in \cite{fouc2016-m1_evolve_n}.
Agreement better than 10\%.
\todo{get accurage M1 numbers from Francois}

\begin{table}%[h]
  \caption{
    Comparison of total luminosities and average energies between
    ray tracing and the M1 transport simulation.
    The ray tracing totals were computed from sums over
    observers placed in the $y$-$z$ plane along an arc at coordinate distance
    $r=250\,{\rm km}$ from the center of the star, at 30 positions
    distributed evenly in $\cos\theta$ over the colatitude range
    $\theta\in[0,90^{\circ}]$.
    M1 values are taken from \cite[Figs. 7, 9, 10]{fouc2016-m1_evolve_n}.
  }
  \label{tab:nsns_rt_vs_m1}
  \begin{tabularx}{\columnwidth}{X r r r}
    & \,\,{\bf RT noscat} & \,\,{\bf RT scat} & \,\,{\bf M1} \\
    \hline
    $L_{\nu_e}\,[10^{52}{\rm erg}\,{\rm s}^{-1}]$        & 5.95 & 6.01 & 5 \\
    $L_{\bar{\nu}_e}$                                    & 10.6 & 11.8 & 12 \\
    $L_{\nu_x}$                                          & 30.2 & 12.6 & 12 \\
    \hline
    $R_{\nu_e}-R_{\bar{\nu}_e}\,[10^{57}{\rm s}^{-1}]$   & -1.06 & -1.86 & -2 \\
    \hline
    $\langle \varepsilon_{\nu_e} \rangle\,[{\rm MeV}]$   & 12.08 & 11.88 & 12 \\
    $\langle \varepsilon_{\bar{\nu}_e} \rangle$          & 15.96 & 14.69 & 15 \\
    $\langle \varepsilon_{\nu_x} \rangle$                & 36.25 & 23.67 & 26 \\
    \hline
  \end{tabularx}
\end{table}
